The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
changes

The International Satisfiability Modulo Theories Competition
(SMT-COMP)~\cite{BdMS05,BdMS07,BDdMOS13,BDOS08,BDOS10,CDW14,CGBD12} is
an annual competition between SMT solvers.  It was instituted in~2005,
and is affiliated with the International Workshop on Satisfiability
Modulo Theories.  Solvers are submitted to the competition by their
developers, and pitted against each other in a number of tracks and
divisions.  The SMT Competition was part of the Federated Logic
Conference (FLoC) Olympic Games, which comprised 14 competitions in
various areas of computational logic, in Vienna in~2014, and again in
Oxford~(UK) in~2018.  It was last described in a 2014 competition
report~\cite{CDW14}.  In this paper, we report on the design and
selected results of the competition during the last FLoC Olympiad,
from 2015 to~2018.

>>>>

The International Satisfiability Modulo Theories Competition
(SMT-COMP)~\cite{BdMS05,BdMS07,BDdMOS13,BDOS08,BDOS10,CDW14,CGBD12} is
an annual competition between SMT solvers.  It was instituted in~2005,
and is affiliated with the International Workshop on Satisfiability
Modulo Theories.  Solvers are submitted to the competition by their
developers, and pitted against each other in a number of tracks and
divisions.

The SMT Competition is one of a growing number of tool competitions in the broad area of formal methods, which are summarised in a recent review of the area~\cite{toolympics}. The two closest competitions in terms of goals and design are the SAT competition (\url{https://www.satcompetition.org/}), which evaluates SAT solvers, and CASC (\url{http://www.tptp.org/CASC/}), which evaluates automated theorem provers (ATPs). In recent years, we have seen a blurring of lines between SMT-COMP and CASC with SMT solvers competing in CASC and ATPs competing in SMT-COMP. The main (informal) distinction remains that SMT-COMP focusses on problems that are heavy in theories, whereas CASC focusses on problems heavy in quantifiers. 
Another closely related competition is SV-COMP (\url{https://sv-comp.sosy-lab.org}) where many tools rely on advanced in SMT solving technology.

The SMT Competition was part of the Federated Logic
Conference (FLoC) Olympic Games, which comprised 14 competitions in
various areas of computational logic, in Vienna in~2014, and again in
Oxford~(UK) in~2018.  It was last described in a 2014 competition
report~\cite{CDW14}.  In this paper, we report on the design and
selected results of the competition during the last FLoC Olympiad,
from 2015 to~2018.
